Fractional Types

### 2016-12-19 typespp.tex
before merge

\unitetl/ :& \mbox{\AE}{\overline{k}}.[\order{\idiso} \circledast \mathbb{T},

@@

The adaptation of the combinators to the pointed dependent setting in Fig .~\ref
{pifracd:comb} is relatively straightforward. First, the types of the
combinators must keep track of how the value currently in focus changes during
evaluation, and hence directly encode the operational semantics of the
language. As suggested above, the quantifiers are interpreted differently
depending on which direction the rule is used. We use a $\forall\exists$
notation to express the presence of \emph{one} quantifier that is interpreted
differently in each direction. The notation has the advantage of being compact,
avoiding duplication, and making the symmetry of the rules explicit. We also
include two new pairs of combinators $\synchl/\packl$ and $\synchr/\packr$ that
serve as explicit quantifier introduction and elimination rules: they serve as
explicit ``synchronization'' points as illustrated in the example below.

@@

Compact closed categories support various interesting constructions, such as
duals, name and coname, and trace, which eventually lead to a certain notion of
recursive higher-order functions~\cite{abramsky-2008}.  We illustrate the
expressiveness of $\Pi^/$ by defining these constructions.

>>>>

\unitetl/ :& \forall\exists{\overline{k}}.[\order{\idiso} \circledast \mathbb{T},

@@

The adaptation of the combinators to the pointed dependent setting in Fig .~\ref
{pifracd:comb} is relatively straightforward. First, the types of the
combinators must keep track of how the value currently in focus changes during
evaluation, and hence directly encode the operational semantics of the
language. As suggested above, the quantifiers are interpreted differently
depending on which direction the rule is used. We use a $\forall\exists$
notation to express the presence of \emph{one} quantifier that is interpreted
differently in each direction. The notation has the advantage of being compact,
avoiding duplication, and making the symmetry of the rules explicit. We also
include two new pairs of combinators $\synchl/packl$ and $\synchr/packr$ that
serve as explicit quantifier introduction and elimination rules: they serve as
explicit ``synchronization'' points as illustrated in the example below.

@@

Compact closed categories support various interesting constructions, such as
duals, name and coname, and trace, which eventually lead to a certain notion of
recursive higher-order functions~\cite{abramsky-2008}.  We illustrate the
expressiveness of $\Pi^/$ by defining duals, name and coname, and a higher-order
\emph{apply} combinator.
